Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute rate.grade based on d_transcript_augmented for constistency

@@

```{r}
#
# Probability of failing, having a low grade

#
# Probability oh having a grade equal or lower than x
d_support$G <- d_transactions$taken_PF_HL %>%
  group_by(
    item
    ) %>%
  summarise(
    `0`    = mean(Grade <= 0),
    `1`    = mean(Grade <= 1),
    `2`    = mean(Grade <= 2),
    `3`    = mean(Grade <= 3),
    `4`    = mean(Grade <= 4),
    `5`    = mean(Grade <= 5),
    `6`    = mean(Grade <= 6),
    `7`    = mean(Grade <= 7),
    `8`    = mean(Grade <= 8),
    `9`    = mean(Grade <= 9),
    `10`   = mean(Grade <= 10)
    ) %>%
  gather(
    key   = grade_ceil,
    value = support.grade,
    `0` : `10`,
    convert = TRUE
    )
```

>>>>

```{r d_support G}
d_support$G <- d_transcript_augmented %>%

  summarise(
    `0`    = mean(Grade <= 0),
    `1`    = mean(Grade <= 1),
    `2`    = mean(Grade <= 2),
    `3`    = mean(Grade <= 3),
    `4`    = mean(Grade <= 4),
    `5`    = mean(Grade <= 5),
    `6`    = mean(Grade <= 6),
    `7`    = mean(Grade <= 7),
    `8`    = mean(Grade <= 8),
    `9`    = mean(Grade <= 9),
    `10`   = mean(Grade <= 10)
  ) %>%

  gather(grade_ceil, rate.grade, `0` : `10`, convert = TRUE)
```

@@
